---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# reviewer
Improving the track changes and reviewing experience in R markdown. `reviewer` provides two main functions:

- an RStudio addin that adds the required JavaScript code to an rmarkdown document, so that when rendered to HTML it can be annotated using the Hypothes.is service
- the capability to compare two versions of an rmarkdown document and display their differences in a nicely-formatted manner.

## Installation

You can install the development version of `reviewer` from [GitHub](https://github.com/ropenscilabs/reviewer) with:

```{r eval = FALSE}
remotes::install_github("ropenscilabs/reviewer")
```

## Annotating web pages

### Important note
In order to use the annotation functionality it is needed to sign-up at [the Hypothes.is website](https://hypothes.is/signup)

----

## Differences between rmarkdown files

The `diff_rmd` function can be used to produce a nicely-formatted document showing the differences between two rmarkdown files. For the purposes of demonstration, we'll use the example files bundled with the package. We'll compare `modified_file` to its earlier version `reference_file`:

```{r exfile1}
modified_file <- system.file("extdata/CheatSheet-modified.Rmd", package = "reviewer")
reference_file <- system.file("extdata/CheatSheet.Rmd", package = "reviewer")
```

```{r exfile2, echo = FALSE}
## for demo purposes, just take the first few lines of these files
tempfile1 <- tempfile()
writeLines(head(readLines(modified_file), 14), con = tempfile1)
modified_file <- tempfile1
tempfile2 <- tempfile()
writeLines(head(readLines(reference_file), 12), con = tempfile2)
reference_file <- tempfile2
```

Compare:

```{r dodiff, eval = FALSE}
library(reviewer)
result <- diff_rmd(modified_file, reference_file)
```

And our output (note that the styling is different in the GitHub README to the output you will see in a standalone HTML document output):

```{r dodiff-hidden, echo = FALSE}
## some minor trickery to make the rendered output appear properly in the README.md
library(reviewer)
result <- diff_rmd(modified_file, reference_file, css = NULL)
htmltools::includeHTML(result$raw)
```

We can also compare the current version of a document to a previous version in stored in a git repository. (These examples are not run here).

If a `reference_file` argument is not provided, by default the `modified_file` will be compared to the most recent copy in the git repo:

```{r diff-ex-2, eval = FALSE}
result <- diff_rmd(modified_file)
```

Or we can compare it to how it appeared in the git repository after a particular commit (here, the commit with reference 750ab4):

```{r diff-ex-3, eval = FALSE}
result <- diff_rmd(modified_file, "750ab4")
```


## Related packages

- [trackmd](https://github.com/ropenscilabs/trackmd) is similar to `reviewer`, but:

  - is an RStudio-specific addin, whereas `reviewer` can be used outside of the RStudio environment (e.g. with your preferred text editor)
  - shows changes only in the *rendered* rmarkdown file (i.e. once it has been converted to its HTML document format). `reviewer` can show changes in either the raw rmarkdown document or its rendered output.

- [latexdiffr](https://github.com/hughjonesd/latexdiffr) similarly shows differences in the *rendered* document, but uses the `latexdiff` utility to do so (you need `latexdiff` installed on your system to use it). It can also be used outside of RStudio.

- [diffobj](https://github.com/brodieG/diffobj) provides a colourized depiction of the differences between arbitrary R objects. This could be used to compare two rmarkdown documents by e.g. reading their contents into character vectors and applying the `diffChr` function.

- [rmdrive](https://github.com/ekothe/rmdrive) allows easy round-tripping of an rmarkdown document to Google Drive, where it can be edited by non-R-using collaborators, and back again. The edited changes could then be viewed using `reviewer`.

- [markdrive](https://github.com/MilesMcBain/markdrive) is similar to `rmdrive`, but pushes the *rendered* rmarkdown document to and from Google.
