---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# reviewer
Improving the track changes and reviewing experience in R markdown

## Installation

You can install the released version of reviewer from [GitHub](https://github.com/ropenscilabs/reviewer) with:

``` r
remotes::install_github("ropenscilabs/reviewer")
```

## Annotating web pages

### Important note
In order to use the annotation functionality it is needed to sign-up at [the Hypothe.is website](https://hypothes.is/signup)

----

## Differences between rmarkdown files

The `diff_rmd` function can be used to produce a nicely-formatted document showing the differences between two rmarkdown files. For the purposes of demonstration, we'll use the example files bundled with the package. We'll compare `modified_file` to its earlier version `reference_file`:

```{r exfile1}
modified_file <- system.file("extdata/CheatSheet-modified.Rmd", package = "reviewer")
reference_file <- system.file("extdata/CheatSheet.Rmd", package = "reviewer")
```

```{r exfile2, echo = FALSE}
## for demo purposes, just take the first few lines of these files
tempfile1 <- tempfile()
writeLines(head(readLines(modified_file), 12), con = tempfile1)
modified_file <- tempfile1
tempfile2 <- tempfile()
writeLines(head(readLines(reference_file), 12), con = tempfile2)
reference_file <- tempfile2
```

Compare:

```{r dodiff, eval = FALSE}
library(reviewer)
result <- diff_rmd(modified_file, reference_file)
```
<style>
pre {
 white-space: pre-wrap;       /* css-3 */
 white-space: -moz-pre-wrap;  /* Mozilla, since 1999 */
 white-space: -pre-wrap;      /* Opera 4-6 */
 white-space: -o-pre-wrap;    /* Opera 7 */
 word-wrap: break-word;       /* Internet Explorer 5.5+ */
 }
</style>
<div style="border:1px solid black; padding: 12px;">
<pre>
```{r dodiff_hidden, echo = FALSE, results = "asis"}
## some trickery to display the modified rmarkdown
## render it to markdown document and include that
library(reviewer)
result <- diff_rmd(modified_file, reference_file, keep_intermediate = TRUE)
txt <- readLines(result$intermediate)
cat(txt, sep = "\n")
```
</pre>
</div>

We can also compare the current version of a document to a previous version in stored in a git repository. (These examples are not run here)

```{r diff-ex-2, eval = FALSE}
## by default the modified_file will be compared to the most recent copy
##  in the git repo
result <- diff_rmd(modified_file)

## or we can compare it to how it appeared in the git repository after a
##  particular commit (here, the commit with reference 750ab4)
result <- diff_rmd(modified_file, "750ab4")
```


