---
title: "Reviewer"
author: "Amy Stringer, Ben Raymond, Mark Dulhunty, Laura de Jong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{reviewer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Differences between rmarkdown files

The `diff_rmd` function can be used to produce a nicely-formatted document showing the differences between two rmarkdown files. For the purposes of demonstration, we'll use the example files bundled with the package. We'll compare `modified_file` to its earlier version `reference_file`:

```{r exfile1}
modified_file <- system.file("extdata/CheatSheet-modified.Rmd", package = "reviewer")
reference_file <- system.file("extdata/CheatSheet.Rmd", package = "reviewer")
```

```{r exfile2, echo = FALSE}
## for demo purposes, just take the first few lines of these files
tempfile1 <- tempfile()
writeLines(head(readLines(modified_file), 14), con = tempfile1)
modified_file <- tempfile1
tempfile2 <- tempfile()
writeLines(head(readLines(reference_file), 12), con = tempfile2)
reference_file <- tempfile2
```

Compare:

```{r dodiff, eval = FALSE}
library(reviewer)
result <- diff_rmd(modified_file, reference_file)
```

And our output:

```{r dodiff-hidden, echo = FALSE}
## some minor trickery to make the rendered output appear properly in the README.md
library(reviewer)
result <- diff_rmd(modified_file, reference_file)
htmltools::includeHTML(result$raw)
```

We can also compare the current version of a document to a previous version in stored in a git repository. (These examples are not run here).

If a `reference_file` argument is not provided, by default the `modified_file` will be compared to the most recent copy in the git repo:

```{r diff-ex-2, eval = FALSE}
result <- diff_rmd(modified_file)
```

Or we can compare it to how it appeared in the git repository after a particular commit (here, the commit with reference 750ab4):

```{r diff-ex-3, eval = FALSE}
result <- diff_rmd(modified_file, "750ab4")
```


<script src="https://hypothes.is/embed.js" async></script>
